A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-01-13 manuscript.Rmd
load repro earlier

---
title: "A Hitchhiker's Guide to Reproducible Research" # replace with something serious
output: pdf_document
repro:
  packages:
    - usethis
---

@@

```r
if(!requireNamespace("remotes"))install.packages("remotes")
remotes::install_github("aaronpeikert/repro")
```

@@

```{r}
library("repro")
check_git()
```

>>>>

---
title: "A Hitchhiker's Guide to Reproducible Research" # replace with something serious
output: pdf_document
repro:
  packages:
    - usethis
    - repro
---

@@

```r
if(!requireNamespace("remotes"))install.packages("remotes")
remotes::install_github("aaronpeikert/repro")
library("repro")
```

@@

```{r}
check_git()
```
